---
title: "SV-Lab10"
output: html_document
date: "2022-10-17"
---

```{r}
#install.packages('ggplot2')
library(ggplot2)
```
```{r}
#install.packages("ISLR")
library(ISLR)
```
Q1.
```{r}
data("Carseats")
str(Carseats)
ggplot(Carseats, aes(x = Price, y = Sales)) +
  geom_point()
```
1b.
```{r}
ggplot(Carseats, aes(x = Price, y = Sales)) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt')
```

1c.
```{r}
ggplot(Carseats, aes(x = Price, y = Sales)) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt') +
  ylab('Sales in thousands')
```

1d.
```{r}
ggplot(Carseats, aes(x = Price, y = Sales)) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt') +
  ylab('Sales in thousands') +
  geom_smooth(method = 'lm', se = F, col='Red')
```

1e.No clear pattern can be observed
```{r}
ggplot(Carseats, mapping = aes(x = Price, y = Sales, color = as.factor(Urban))) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt') +
  ylab('Sales in thousands')
```

1f. No clear pattern
```{r}
ggplot(Carseats, mapping = aes(x = Price, y = Sales, color = as.factor(US), shape = as.factor(US))) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt') +
  ylab('Sales in thousands')
```

1g. 'Good' ShelveLoc tend to have higher sales than 'Medium' ShelveLoc, while 'Medium' ShelveLoc tend to have higher sales than 'Bad' ShelveLoc
```{r}
ggplot(Carseats, mapping = aes(x = Price, y = Sales, color = ShelveLoc, shape = ShelveLoc)) +
  geom_point() +
  scale_y_continuous(trans = 'sqrt') +
  ylab('Sales in thousands')
```

Q2.
```{r}
data("iris")
str(iris)
ggplot(iris, mapping = aes(x = Petal.Width, y = Sepal.Length)) +
  geom_point()
```

2b. Setosas have smallest petal width and sepal length, while versicolor tend to have bigger petal width and sepal length in comparison.
Virginicas have the biggest petal width and sepal length when compared to both the other species.
```{r}
ggplot(iris, mapping = aes(x = Petal.Width, y = Sepal.Length, color = Species)) +
  geom_point()
```

2c. Petal Length increases with increasing sepal length and increasing petal width; hence, Setosas have the smallest petal length, then versicolor, then virginica with the biggest sepal length.
```{r}
ggplot(iris, mapping = aes(x = Petal.Width, y = Sepal.Length, color = Species, size = as.factor(Petal.Length))) +
  geom_point()
```

Q3.
```{r}
data("College")
str(College)
ggplot(College, mapping = aes(x = Apps, y = Enroll)) +
  geom_point()
```

3b. Yes. There are more enrollment with more applicants
```{r}
ggplot(College, mapping = aes(x = Apps, y = Enroll)) +
  geom_point() +
  scale_x_continuous(trans = 'log') +
  scale_y_continuous(trans = 'log')
```

3c.Public Colleges generally have more applicants than private colleges
```{r}
ggplot(College, mapping = aes(x = Apps, y = Enroll, color = Private)) +
  geom_point() +
  scale_x_continuous(trans = 'log') +
  scale_y_continuous(trans = 'log')
```

3d. No
```{r}
ggplot(College, mapping = aes(x = Outstate, y = Room.Board, color = Books)) +
  geom_point() +
  scale_x_continuous(trans = 'log') +
  scale_y_continuous(trans = 'log')
```

3e Private colleges generally have higher tuiton costs and room and boarding costs than Public colleges.
```{r}
ggplot(College, mapping = aes(x = Outstate, y = Room.Board, color = Private)) +
  geom_point() +
  scale_x_continuous(trans = 'log') +
  scale_y_continuous(trans = 'log')
```